\exercise

Consider the problem which requires to compute the intersection between two
sorted sets $A$ and $B$ of size $n$ and $m$ respectively, $m < n$.
%
\begin{enumerate}
  \item Propose a solution taking $O(n + m)$ time.
  \item Propose a solution taking $O(m \log n)$ time.
  \item Propose a solution taking $O\big(m \big(1 + \log \frac{n}{m}\big)\big)$ time.
  \item Show that the last time bound is optimal in the comparison model.
\end{enumerate}

\solution

\begin{enumerate}

  \item Scan both sets in a merge fashion: let $a_i$ and $b_j$ the $i$-th and
  $j$-th elements of the sequences $A$ and $B$, respectively. If $a_i = b_j$,
  they belong to $A \cap B$, else if $a_i < b_j$ (or $a_i > b_j$), we increase
  $i$ (or $j$), until the end of a sequence. This solution has complexity $O(m +
  n)$.

  \item We take the shorter sequence and for each of its elements we perform a
  binary search on the longer one. This solution has complexity $O(m\log n)$.

  \item We perform an intersection based on mutual partitioning: we take the
  median element of the shorter and search it in the longer one via binary
  search. Then, we perform again this procedure recursively on the remaining
  lower and upper halves. This solution has time complexity $T(m,n) = O(\log n)
  + 2T\big(\frac{n}{2}, \frac{m}{2}\big) = O\big(m \big(1 + \log
  \frac{n}{m}\big)\big)$.

  \item There are $n \choose m$ possible solution to the set intersection
  problem, so every comparison-based algorithm must perform $\Omega\big(\log {n
  \choose m}\big) = \Omega\big(m\log \frac{n}{m}\big)$ steps.

\end{enumerate}
